\chapter{Acknowledgements}

%\lipsum[1-3]

I would first and foremost like to thank my advisors, Greg Rohrer and Paul Salvador, for their support, guidance, and the example they have set during course of my Ph.D. work at Carnegie Mellon. I would also like to thank the members of my committee, Jay Whitacre, Lisa Porter, and Stefan Bernhard for their time and efforts in guiding the work presented in this document. The funding of the National Science Foundation through grant \abbr{DMR}\#0804770 is also gratefully acknowledged.

Throughout my time pursuing my Ph.D., I have benefitted from the support, advice, and friendship of numerous other students in the Department of Materials Science and Engineering. In particular, I'd like to acknowledge the members of my research group, Li Li and Yiling Zhang. Along with Li and Yiling, I'd like to thank the other members of my cohort, Ben Anglin, Patrick Callahan, Clay Stein, and Reeju Pokharel. Thanks also to Stephanie Bojarski, June Bott, Begum Gulsoy, Ayesha Hashambhoy, Ranga Kamaladasa, Ammon Lu, Clare Mahoney, Noey Munprom, Carolyn Norwood, Sutatch Ratanaphan, Ellen Reifler, Erica Sampson, Fatma Uyar, Lu Yan, and all the other members of the department who have made the past four years an enjoyable experience. June Bott deserves particular credit for giving me a place to live in the last few months of my time in Pittsburgh. The staff of the Materials Science and Engineering Department were hugely helpful in my successes. In particular, thanks to Jason Wolf for all his time and guidance, both technical and otherwise. Also thank you to Adam Wise and Tom Nuhfer. Thanks also to Marygrace Antkowski,  Anita Connelly, Angela Pusateri, and Suzy Smith. Lastly, Jeanna Pekarcik deserves infinite thanks for all of her help and conversation throughout the years.

My time with the Graduate Student Assembly has provided some of the most rewarding experiences I've had and best friends I've made while at Carnegie Mellon. Particular thanks to my fellow \abbr{GSA} executive committee members, Dave Bergman, Will Boney, Grace Heckmann, and Jason Imbrogno. Thanks and good luck to my successors on \abbr{GSA} exec, Carolyn Norwood (again) and Ashlie Henery. Lastly, thanks to all the other people I've met through \abbr{GSA}, Emily Carson, Carolyn Denomme, Patrick Foley, Jon Kowalski, Amelia Kriss, Jessica Lyman, Zach Moir, and Ruth Poproski, each of whom contributed to an enjoyable experience at Carnegie Mellon, and probably at least one too many nights at \abbr{PHI}. My joining the Graduate Student Assembly was largely due to the friendship of Patrick Kelley, my first and best friend at Carnegie Mellon. 

Carnegie Mellon University is a uniquely stimulating place to attend graduate school. That it remains so is due to the hard work of numerous members of the university administration. I have had the pleasure of working with many of these people during my time with \abbr{GSA}, and am continually impressed by their devotion to improving the graduate student experience. In particular, Suzie Laurich-McIntire and the Office of Graduate Education deserves the thanks of every graduate student. I would also like to thank Amy Burkert, Gina Casalegno, Jared Cohon, Holly Hippensteel, Lisa Krieg, Michael Murphy, Kaycee Palko, and Gloriana St. Clair for their service to the university and its graduate students.

Lastly, and most importantly, thank you to my family, including my parents, Mike Schultz and Amy Thomas for their support and encouragement, not least of which being the financial support of my education. Also a sincere thank you to my sister and friend, Laura Schultz. I was raised in an environment conducive to learning, and I am continually thankful for the opportunities they have given me. Those opportunities are largely responsible for the person I am today.


{\raggedleft{\scshape Andy Schultz} \\ Pittsburgh, PA \\ September 2012\par}
